Tissue-Exclusive Proteins Report

### 2022-06-20 EnrichR.Rmd
happy pride month

setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")

@@

setEnrichrSite("Enrichr") # human genes???
dbs = c("GO_Molecular_Function_2018", "GO_Cellular_Component_2018", "GO_Biological_Process_2018")

enriched = enrichr(sec_Ssec_brain[1:100,], dbs)

>>>>

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

tesec_brain = read.csv("TE.Sec_Ssec_brain.csv")
tesec_liver = read.csv("TE.Sec_Ssec_liver.csv")
tensec_brain = read.csv("TE.NSec_Ssec_brain.csv")
tensec_liver = read.csv("TE.NSec_Ssec_liver.csv")
bicor_brain = read.csv("Bicor_brain.csv")
bicor_liver = read.csv("Bicor_liver.csv")

fix.read.csv = function(x)
{
  names = x[,1]
  gee = x[,2:dim(x)[2]]
  rownames(gee) = names
  return(gee)
}

tesec_brain = fix.read.csv(tesec_brain)
tesec_liver = fix.read.csv(tesec_liver)
tensec_brain = fix.read.csv(tensec_brain)
tensec_liver = fix.read.csv(tensec_liver)
bicor_brain = fix.read.csv(bicor_brain)
bicor_liver = fix.read.csv(bicor_liver)

@@

#setEnrichrSite("Enrichr") # human genes???
#dbs = c("GO_Molecular_Function_2018", "GO_Cellular_Component_2018", "GO_Biological_Process_2018")
dbs = c("MSigDB_Computational", "MSigDB_Hallmark_2020", "MSigDB_Oncogenic_Signatures")
fin = c()
for(i in 1:174)
{
  names = colnames(bicor_brain[,bicor_brain[i,] < 0.05])
  enriched = enrichr(tesec_brain[, 1], dbs)
  if(dim(enriched$MSigDB_Computational)[1] != 0 | dim(enriched$MSigDB_Hallmark_2020)[1] != 0 | dim(enriched$MSigDB_Oncogenic_Signatures)[1] != 0 )
  {
    fin = c(fin, i)
  }
}

### 2022-06-20 Partial Correlation Ssec Values.Rmd
happy pride month

Problem with Keller- no code, no explanation of how they computed PaCor analytically

Problem with partial correlation methods- don't like that there are more genes than subjects

@@

setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

@@

```
Wow what a cluster fuck
```{r, echo = FALSE, eval = FALSE}

# PaCor v. BiCor
# pcor(target, tes) - pull out tes genes?
target_liver = cbind(tes.liver, tens.liver)
pacor.brain_data = cbind(tes.brain, target_liver)
pacor.brain = pcor(pacor.brain_data, method = "spearman")

#########
library(psych)

pacor.brain = partial.r(pacor.brain_data, method = "spearman")

p.pacor.brain = corr.p(pacor.brain, n = 577, ci = FALSE)$p

fin.pacor.brain = p.pacor.brain[rownames(p.pacor.brain) %in% colnames(tes.brain), colnames(p.pacor.brain) %in% colnames(target_liver)]

scores = rowSums(-log(fin.pacor.brain))

pacor_Ssec_brain = data.frame(Gene_symbol = names(scores), score = scores) %>%
  #filter(Gene_symbol %in% sec_annot$ensembl_gene_id) %>%
  mutate(Ssec = score / length(colnames(target_liver))) %>%
  dplyr::select(-score) %>%
  arrange(desc(Ssec))

###
sum = c()
for (i in colnames(tes.brain))
{
  pacor.brain = partial.r(cbind(tes.brain[,i], target_liver), method = "spearman")

  p.pacor.brain = corr.p(pacor.brain, n = 404, ci = FALSE)$p

  sum = c(sum, sum(p.pacor.brain[1,]))
}
```

These don't like that there are more genes than subjects :(

partial.r {psych}	R Documentation
Find the partial correlations for a set (x) of variables with set (y) removed.
Description
A straightforward application of matrix algebra to remove the effect of the variables in the y set from the x set. Input may be either a data matrix or a correlation matrix. Variables in x and y are specified by location. If x and y are not specified, then the effect of all variables are partialled from all the other correlations. May also be done using formula input which is more convenient when comparing results to regression models

Usage
partial.r(data, x, y, use="pairwise",method="pearson")
Arguments
data	
A data or correlation matrix

x	
The variable names or locations associated with the X set (or formula input)

y	
The variable names or locations associated with the Y set to be partialled from the X set

use	
How should we treat missing data? The default is pairwise complete.

Warning in cor.smooth(R) :
  Matrix was not positive definite, smoothing was done
In smc, smcs < 0 were set to .0

####

pcor {ppcor}	R Documentation
Partial correlation
Description
The function pcor can calculate the pairwise partial correlations for each pair of variables given others. In addition, it gives us the p value as well as statistic for each pair of variables.

Usage
pcor(x, method = c("pearson", "kendall", "spearman"))
Arguments
x	
a matrix or data fram.

method	
a character string indicating which partial correlation coefficient is to be computed. One of "pearson" (default), "kendall", or "spearman" can be abbreviated.

@@

estimate = ggm.estimate.pcor(pacor.brain_data, method = "static", lambda = 0)
edge = network.test.edges(estimate)

>>>>

Lambda???

@@

setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

@@

@@

target_liver = cbind(tes.liver, tens.liver)

pacor.ssec.brain = c()

for (i in 1:174)
{
  test = data.frame(tes.brain[,i], target_liver)
  estimate = ggm.estimate.pcor(test, method = "static")
  edge = network.test.edges(estimate) # pvalue may be fdr... :P, but i guess it doesn't matter??

  # calculate ssec

  this = edge[edge$node1 == 1,]
  score = sum(-log(this$pval))/length(target_liver)

  pacor.ssec.brain = c(pacor.ssec.brain, score) 
}

```{r, echo = FALSE, eval = FALSE}

# ARCHIVE BAD STUFF

test = data.frame(tes.brain[,1], target_liver)
estimate = ggm.estimate.pcor(test, method = "static") #, lambda = 0) # lambda??
edge = network.test.edges(estimate)

### 2022-06-20 SeldinReport.Rmd
happy pride month

brain.liv = bicorAndPvalue(ts_protein_brain, target_liver, use = 'pairwise.complete.obs')
# brain.liv$p

@@

>>>>

brain.liv = bicorAndPvalue(ts_protein_brain, target_liver, use = 'pairwise.complete.obs')

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
write.csv(brain.liv$p, "Bicor_brain.csv")
# brain.liv$p

@@

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
write.csv(liv.brain$p, "Bicor_liver.csv")

### 2022-06-20 Tissue Exclusive Flow Chart.Rmd
happy pride month

grid.newpage()
txt1 =
"All Normalized Expression Values
Brain (18,385 genes)
Liver (15,365 genes)"
boxAR = boxGrob(txt1, x = 0.15, y = 0.5)
txt4 = 
  "Protein-Coding Genes Only
Brain (16,457 genes)
Liver (14,109 genes)"
boxPC = boxGrob(txt4, x = 0.35, y = 0.5)
txt5 = 
  "Secreted Protein-Coding Genes
Brain (657 genes)
Liver (818 genes)"
boxSe = boxGrob(txt5, x = 0.35, y = 0.70)
txt6 = 
  "Tissue-Exclusive, Secreted 
  Protein-Coding Genes
Brain (174 genes)
Liver (35 genes)"
boxTES = boxGrob(txt6, x = 0.55, y = 0.70)
txt7 = 
  "Non-Secreted Protein-Coding Genes
Brain (15,800 genes)
Liver (13,591 genes)"
boxNSe = boxGrob(txt7, x = 0.35, y = 0.30)
txt8 = 
  "Tissue-Exclusive, Non-Secreted 
  Protein-Coding Genes
Brain (2,589 genes)
Liver (371 genes)"
boxTENS = boxGrob(txt8, x = 0.55, y = 0.30)
txt9 = 
  "Tissue-Exclusive 
  Protein-Coding Genes
Brain (2,751 genes)
Liver (405 genes)"
boxTE = boxGrob(txt8, x = 0.55, y = 0.5)

>>>>

grid.newpage()
txt1 =
"All Normalized Expression Values
Brain (18,385 genes)
Liver (15,365 genes)"
boxAR = boxGrob(txt1, x = 0.15, y = 0.5)
txt4 = 
  "Protein-Coding Genes Only
Brain (16,457 genes)
Liver (14,109 genes)"
boxPC = boxGrob(txt4, x = 0.35, y = 0.5)
txt5 = 
  "Secreted Protein-Coding Genes
Brain (657 genes)
Liver (518 genes)"
boxSe = boxGrob(txt5, x = 0.35, y = 0.70)
txt6 = 
  "Tissue-Exclusive, Secreted 
  Protein-Coding Genes
Brain (174 genes)
Liver (35 genes)"
boxTES = boxGrob(txt6, x = 0.55, y = 0.70)
txt7 = 
  "Non-Secreted Protein-Coding Genes
Brain (15,800 genes)
Liver (13,591 genes)"
boxNSe = boxGrob(txt7, x = 0.35, y = 0.30)
txt8 = 
  "Tissue-Exclusive, Non-Secreted 
  Protein-Coding Genes
Brain (2,577 genes)
Liver (368 genes)"
boxTENS = boxGrob(txt8, x = 0.55, y = 0.30)
txt9 = 
  "Tissue-Exclusive 
  Protein-Coding Genes
Brain (2,751 genes)
Liver (403 genes)"
boxTE = boxGrob(txt8, x = 0.55, y = 0.5)
